Fréchet Distance

### 2022-12-23 docs/paper.tex
figure as pdf file
Revert "removed name for peer review"
This reverts commit 4843b9037e25fbab2e8b778999e10609656f7d27.
minor (typo) fixes from peer review

\usepackage{svg}

@@

To quantify the similarity of two given curves (e.g. shapes, paths, or trajectories)
a distance metric can be used. 
We can't simply use a distance metric like euclidean distance 
because we don't want to compare points to points 
but instead compare curves to curves. 
Therefore, we start by defining curves in \autoref{def_curve}.

@@

\begin{mydef}
  \label{def_hausdorff_distance}
  Given two normal or polygonal curves $P$ and $Q$, 
  their Hausdorff distance $\delta_{hd}(P,Q)$ is mathematically defined as: 
  $$\delta_{hd}(P,Q) = \max \left( \sup_{p \in P} \inf_{q \in Q} \text{dist}(p,q), \sup_{q \in Q} \inf_{p \in P} \text{dist}(p,q) \right)$$
\end{mydef}

The Hausdorff distance metric $\delta_{hd}(P,Q)$ defined in \autoref{def_hausdorff_distance} 
is very intuitive and can be easily computed for polygonal curves \cite{ko_complexity_2013}.
It finds applications in computer vision and computer graphics 
where it is used to compare the similarity of two mesh objects \cite{cignoni_metro_1998,ko_complexity_2013}. 
However, this metric does not take the course of the curves into account, 
but only the point sets of the individual curves.
Two curves may have a small Hausdorff-distance but seem very dissimilar 
when looking at them, see \autoref{fig_hausdorff_distance_bad_example}.

@@

% Fréchet distance motivation
In reality, the course of the curves is important for many applications. 
For example, in handwriting character recognition on digital input devices, especially in Chinese \cite{chanin_david_hanzi_nodate},
gesture recognition on smartphone touchscreens \cite{hu_research_2022}, % TODO: add more citations
and motion evaluation in real-time motion capturing \cite{qiao_real-time_2017, shehu_curve_2012}. % TODO: add more citations
For this reason, the \textit{Fréchet distance}, named after the famous French mathematician René Maurice Fréchet, was introduced.

@@

% continuous Fréchet distance equation
\begin{mydef}
  \label{def_frechet_distance}
  Given two (polygonal) curves $P: [a,a'] \mapsto V$, $Q: [b,b'] \mapsto V$ and a distance function $\text{dist}: (V,V) \mapsto \mathbb{R}$, 
  their Fréchet distance $\delta_{F}(P,Q)$ is mathematically defined as: 
  $$\delta_{F}(P,Q) = \inf_{\substack{\alpha: [0,1] \mapsto [a, a'] \\ \beta: [0,1] \mapsto [b, b']}} \max_{t \in [0,1]} \text{dist}(P(\alpha(t)), Q(\beta(t)))$$
  where $\alpha$ and $\beta$ represent the walking speed as 
  continuous monotonically increasing functions with
  $\alpha(0) = a, \alpha(1) = a'$, 
  $\beta(0) =b, \beta(1) =b'$.
\end{mydef}

\begin{figure}[ht]
  \centering
  % TODO: Add example graphic of Frechet distance
  % \includegraphics[width=\textwidth]{images/hausdorff/hausdorff-distance-example.pdf}
  \includesvg{images/frechet_distance/frechet-distance-example.svg}
  \caption{The Fréchet distance is indicated by the black lines connecting the two polygonal curves.}
  \label{fig_frechet_distance_example}
\end{figure}

% TODO: merge with above mentions of applications?
Besides the previously mentioned applications, 
where the course of the curves is important, 
the Fréchet distance also finds applications in
(online) handwriting signature verification \cite{zheng_algorithm_2008,fang_research_2018},
map-matching tracking data for traffic control, routing and navigation \cite{wenk_addressing_2006,brakatsoulas_map-matching_2005},
and moving object analysis, e.g., detecting commuting patterns \cite{buchin_detecting_2011}.

@@

\subsection{Weak Fréchet Distance}
\label{sec_weak_frechet_distance}
The \textit{weak Fréchet distance} (non-monotone Fréchet distance) 
slightly modifies the continuous version by allowing going backwards. 
The definition remains the same as for the continuous Fréchet distance in \autoref{def_frechet_distance}
where the monotonicity of $\alpha$ and $\beta$ is no longer required.
Note that they are still required to be continuous and have the correct starting and ending values.
% TODO: Add use cases
The weak Fréchet distance is a lower bound on the continuous Fréchet distance.
However, the Ratio between them may be arbitrarily large, 
as can be seen by the structure given in \autoref{fig_weak_frechet_distance}. \cite{alt_computing_1995}

@@

\begin{mydef}
  \label{def_point_coupling}
  A \textit{coupling} L between two polygonal curves $P$ and $Q$, 
  with points $(u_1, \dots, u_p)$ and $(v_1, \dots, v_p)$ respectively, 
  is defined as a sequence
  $$(u_{a_1}, v_{b_1}),(u_{a_2}, v_{b_2}), \dots, (u_{a_m}, v_{b_m})$$
  such that $a_1 = 1, b_1 = 1, a_m = p, b_m = q$ 
  while preserving order and the jump length limitation.
  % Note different definiton than in original paper
  % fixes error for unequal length polygonal curves
  Thus, for all $i \in \{1, \dots m-1\}$
  the jump length should be positive but no more than 1,
  i.e., $0 \leq a_{i+1} - a_i \leq 1$ (respectively $0 \leq b_{i+1} - b_i \leq 1$).
\end{mydef}

@@

The discrete variation (\autoref{def_discrete_frechet_distance}) gives an upper bound on the continuous Fréchet distance (\autoref{def_frechet_distance}). 
% Clearify if this is really an upper bound for polygonal curves with example
This might not be very obvious for the case of polygonal curves, 
but \autoref{fig_frechet_distance_upper_bound_example} gives an intuitive example.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\textwidth]{images/frechet_distance/discrete-frechet-distance-upper-bound.pdf}
  \caption[Upper bound on Fréchet distance]{
    In the case of the discrete Fréchet distance 
    one frog has to wait at either start or end $Q$
    while the other one is at the middle vertex of $P$, 
    thus requiring a minimal length of $\sqrt{d^2 + l^2}$ for any coupling.
    In contrast, a leash of length $d$ is sufficient for the continuous Fréchet distance.}
  \label{fig_frechet_distance_upper_bound_example}
\end{figure}

Additionally, it's also a lower bound on the continuous Fréchet distance 
plus the distance of the longest legal jump of any frog. 
By increasing the number of points of a polygonal curve that 
over approximates some other polygonal curve
this property can be used to compute the continuous Fréchet distance \cite{eiter_computing_1994}.

@@

\section{Algorithms}
\label{sec_algorithms}
% Chapter summary and structure
Several algorithms to compute the Fréchet distance of polygonal curves were proposed, 
starting from the Original algorithm for the continuous variant by Alt and Godau in 1995 \cite{alt_computing_1995}.
The algorithm is based on a concept called free-space diagram and gives a baseline for newer improved versions, 
e.g., the version by Buchin et al. \cite{buchin_four_2017}. 
This chapter is structured as follows: 
first the original algorithm for the continuous Fréchet distance is described in \autoref{sec_original_algorithm}.
% then in \autoref{sec_improved_algorithm} a more recent improved algorithm for the same problem is given.
Afterwards, the modification necessary to compute the weak variant are described in \autoref{sec_weak_algorithm}.
Finally, an algorithm to compute the discrete Fréchet distance is given in \autoref{sec_discrete_algorithm}.

@@

We start by looking at the simplest case for two polygonal curves with two vertices each, i.e., two line segments.
The free space is all valid combinations of positions on $P$ and $Q$ that have a distance of at most $\varepsilon$.
Therefore, we define $F_\varepsilon = \{(s,t) \in [0,1]^2 \ | \ dist(P(s), Q(t)) \leq \varepsilon \}$.
Plotting $s$ and $t$ on a two-dimensional graph, while indicating all illegal combinations in 
another color, gives the free space diagram, see \autoref{fig_free_space}. \cite{alt_computing_1995}

@@

Computing the complete free space $F_\varepsilon$ is very compute intensive 
because each point in the continuous space needs to be computed. 
Using the convexity property of each cell in the free space,
we can observe that only a small constant number of points need to be computed per cell. 
These points define the legal regions on each boundary side of the cell, see \autoref{fig_legal_boundary_intervals_of_a_cell}. 
We don't need to know the exact shape of the free space 
because we travel in a monotonically increasing way through a convex space,
hence never entering any illegal regions.

@@

Due to the constant number of intersection points required per cell, 
the free space of a single cell can be computed in $\mathcal{O}(1)$ time.
Therefore, the complete free space of all cells can be computed in $\mathcal{O}(pq)$
because there are $p-1$ (respectively $q-1$) edges in $P$ (respectively $Q$).

@@

Another approach is to check all values of $\varepsilon$ where something ``interesting'' happens
until the smallest value of $\varepsilon$ is obtained where a monotonically increasing path 
from $(0,0)$ to $(p,q)$ in $F_\varepsilon$ exists.
We will call these the \textit{critical values} of $\varepsilon$, which are:
\begin{enumerate}
  \item the minimal value of $\varepsilon$ where $(0,0) \in F_\varepsilon$ and $(p,q) \in F_\varepsilon$.
  \item values of $\varepsilon$ where a new passage on the border edge 
        between two neighboring cells opens up.
  \item values of $\varepsilon$ where a new passage horizontal (respectively vertical) passage 
        between two non-neighboring cells opens up.
\end{enumerate}

@@

% Algorithms for different variants
\subsection{Algorithm for the Weak Fréchet Distance}
\label{sec_weak_algorithm}
The weak Fréchet distance, as described in \autoref{sec_weak_frechet_distance},
the computation becomes less complex compared to the continuous Fréchet distance.
Specifically, we can ignore critical values of the third type, 
since it is no longer required to move monotonically 
and one could just go left or down in the free space diagram taking any arbitrary continuous path.
Therefore, the focus shifts towards critical values of the second type, 
those where new passages between neighboring cells open up.
Alt and Godau \cite{alt_computing_1995} proposed two algorithms to compute the weak Fréchet distance.

For both algorithms the problem is modeled as a grid based graph of $p$ by $q$ vertices, 
one for each cell of the free space diagram,
and edges connecting the vertices with their, up to six, neighboring vertices.
Additionally, $s$ is added as start vertex and $t$ as end vertex.
This results in an undirected Graph $G=(V,E)$ 
where $V = \{C_{i,j} \ | \ 0 \leq i \leq p, 0 \leq j \leq q \} \cup \{s,t\}$
and $E=\{(C_{i,j}, C_{i+1,j}) \ | \ \ 0 \leq i < p, 0 \leq j \leq q\} \cup \{(C_{i,j}, C_{i,j+1}) \ | \ \ 0 \leq i \leq p, 0 \leq j < q\} \cup \{(s, C_{0,0}), (C_{p,q}, t)\}$.
Each edge $(C_{i,j}, C_{i',j'})$ is assigned a critical minimal value of $\varepsilon$ 
such that there is a passage through the border between two cells in the free space. 
Furthermore, the minimal value of $\varepsilon$ such that $(0,0) \in F_\varepsilon$ is assigned to the first edge $(s, C_{0,0})$ 
and the minimal value of $\varepsilon$ such that $(p,q) \in F_\varepsilon$ is assigned to the last edge $(C_{p,q}, t)$. \cite{alt_computing_1995}

The first algorithm is again based on first solving the decision problem 
and then searching for the right $\varepsilon$ through binary search.
The decision problem is satisfied, if and only if there exists a path from $s$ to $t$ in $G$ 
with a maximum single edge value of $\varepsilon$.
This can be checked by removing all edged with values greater than $\varepsilon$ from $E$ 
and then checking if $s$ is still connected to $t$. 
This can be done through some graph traversal algorithm like breadth-first search or depth-first search
in $\mathcal{O}(pq)$ time. \cite{alt_computing_1995}
Since the number of critical values is no longer dominated by the third case,
rather by the second case of $\mathcal{O}(pq)$ values, 
the overall computation problem can be solved in $\mathcal{O}(pq \log (pq))$ time using binary search \cite{van_leusden_novel_2013}.

@@

\begin{mydef}
  \label{def_recursive_forumla_discrete_frechet_distance}
  The discrete Fréchet distance of polygonal curves $P' = (u_1, \dots, u_i)$ and $Q' = (v_1, \dots, v_j)$
  can be computed by
  \begin{align*}
    c(i,j) &= \begin{cases}
      dist(u_1, v_1), &\text{if } i=1 \text{and } j=1 \\
      \max \{c(i-1,j), dist(u_i, v_1)\}, &\text{if } i>1 \text{and } j=1 \\
      \max \{c(i,j-1), dist(u_1, v_j)\}, &\text{if } i=1 \text{and } j>1 \\
      \max \{c(i-1,j), c(i,j-1), c(i-1,j-1), dist(u_i, v_j)\}, &\text{if } i>1 \text{and } j>1
    \end{cases} \\
    &= \delta_{dF}(P',Q')
  \end{align*}
\end{mydef}

\section{Conclusion}
% Which version to use when
This work gives an overview on the Fréchet distance, 
its variants and algorithms to compute them. 
Several differences between the variants have been described 
and evaluated. 
In conclusion, it can be stated that computing the continuous 
Fréchet distance is more computationally expensive compared 
to its discrete and weak variants.
However, computing the continuous variant can be done efficiently
in practice by binary searching the bits of the desired accuracy directly
instead of computing the formally correct value. 
Alternatively, the discrete Fréchet distance can be calculated, 
since it constrains the continuous distance 
from below and above. 
In this way, the tolerance range can be narrowed down.

>>>>

% \usepackage{svg}

@@

To quantify the similarity of two given curves (e.g. shapes, paths, or trajectories)
a distance metric can be used. 
We can not simply use a distance metric like euclidean distance 
because we do not want to compare points to points 
but instead compare curves to curves. 
Therefore, we start by defining curves in \autoref{def_curve}.

@@

\begin{mydef}
  \label{def_hausdorff_distance}
  Given two normal or polygonal curves $P$ and $Q$, 
  their Hausdorff distance $\delta_{hd}(P,Q)$ is defined as: 
  $$\delta_{hd}(P,Q) = \max \left( \sup_{p \in P} \inf_{q \in Q} \text{dist}(p,q), \sup_{q \in Q} \inf_{p \in P} \text{dist}(p,q) \right)$$
\end{mydef}

The Hausdorff distance metric $\delta_{hd}(P,Q)$ defined in \autoref{def_hausdorff_distance} 
is very intuitive and can be easily computed for polygonal curves \cite{ko_complexity_2013}.
It finds applications in computer vision and computer graphics 
where it is used to compare the similarity of two mesh objects \cite{cignoni_metro_1998,ko_complexity_2013}. 
However, this metric does not take the course of the curves into account, 
but only the point sets of the individual curves.
Two curves may have a small Hausdorff distance but seem very dissimilar 
when looking at them, see \autoref{fig_hausdorff_distance_bad_example}.

@@

% Fréchet distance motivation
In reality, the course of the curves is important for many applications. 
For example, 
in handwriting character recognition on digital input devices, especially in Chinese \cite{chanin_david_hanzi_nodate},
(online) handwriting signature verification \cite{zheng_algorithm_2008,fang_research_2018},
gesture recognition on smartphone touchscreens \cite{hu_research_2022}, % TODO: add more citations
map-matching tracking data for traffic control, routing and navigation \cite{wenk_addressing_2006,brakatsoulas_map-matching_2005},
moving object analysis, e.g., detecting commuting patterns \cite{buchin_detecting_2011},
and motion evaluation in real-time motion capturing \cite{qiao_real-time_2017, shehu_curve_2012}. % TODO: add more citations
For this reason, the \textit{Fréchet distance}, named after the famous French mathematician René Maurice Fréchet, was introduced.

@@

% continuous Fréchet distance equation
\begin{mydef}
  \label{def_frechet_distance}
  Given two (polygonal) curves $P: [a,a'] \mapsto V$, $Q: [b,b'] \mapsto V$ and a distance function $\text{dist}: (V,V) \mapsto \mathbb{R}$, 
  their Fréchet distance $\delta_{F}(P,Q)$ is defined as: 
  $$\delta_{F}(P,Q) = \inf_{\substack{\alpha: [0,1] \mapsto [a, a'] \\ \beta: [0,1] \mapsto [b, b']}} \max_{t \in [0,1]} \text{dist}(P(\alpha(t)), Q(\beta(t)))$$
  where $\alpha$ and $\beta$ represent the walking speed as 
  continuous monotonically increasing functions with
  $\alpha(0) = a, \alpha(1) = a'$, 
  $\beta(0) =b, \beta(1) =b'$.
\end{mydef}

\begin{figure}[ht]
  \centering
  % TODO: Add example graphic of Frechet distance
  % \includegraphics[width=\textwidth]{images/hausdorff/hausdorff-distance-example.pdf}
  \includegraphics{images/frechet_distance/frechet-distance-example.pdf}
  \caption{The Fréchet distance is indicated by the black lines connecting the two polygonal curves.}
  \label{fig_frechet_distance_example}
\end{figure}

@@

\subsection{Weak Fréchet Distance}
\label{sec_weak_frechet_distance}
The \textit{weak Fréchet distance} (non-monotone Fréchet distance) 
slightly modifies the continuous version by allowing to go backwards. 
The definition remains the same as for the continuous Fréchet distance in \autoref{def_frechet_distance}
where the monotonicity of $\alpha$ and $\beta$ is no longer required.
Note that they are still required to be continuous and have the correct starting and ending values.
% TODO: Add use cases
The weak Fréchet distance is a lower bound on the continuous Fréchet distance.
However, the ratio between them may be arbitrarily large, 
as can be seen by the structure given in \autoref{fig_weak_frechet_distance}. \cite{alt_computing_1995}

@@

\begin{mydef}
  \label{def_point_coupling}
  A \textit{coupling} L between two polygonal curves $P$ and $Q$, 
  with points $(u_1, \dots, u_p)$ and $(v_1, \dots, v_q)$ respectively, 
  is defined as a sequence
  $$(u_{a_1}, v_{b_1}),(u_{a_2}, v_{b_2}), \dots, (u_{a_m}, v_{b_m})$$
  such that $a_1 = 1, b_1 = 1, a_m = p, b_m = q$ 
  while preserving order and the jump length limitation.
  % Note different definiton than in original paper
  % fixes error for unequal length polygonal curves
  Thus, for all $i \in \{1, \dots m-1\}$
  the jump length should be positive but no more than 1,
  i.e., $0 \leq a_{i+1} - a_i \leq 1$ (respectively $0 \leq b_{i+1} - b_i \leq 1$).
\end{mydef}

@@

The discrete variant (\autoref{def_discrete_frechet_distance}) gives an upper bound on the continuous Fréchet distance (\autoref{def_frechet_distance}). 
% Clearify if this is really an upper bound for polygonal curves with example
This might not be very obvious for the case of polygonal curves, 
but \autoref{fig_frechet_distance_upper_bound_example} gives an intuitive example.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\textwidth]{images/frechet_distance/discrete-frechet-distance-upper-bound.pdf}
  \caption[Upper bound on Fréchet distance]{
    In the case of the discrete Fréchet distance 
    one frog has to wait at either start or end of $Q$
    while the other one is at the middle vertex of $P$, 
    thus requiring a minimal length of $\sqrt{d^2 + l^2}$ for any coupling.
    In contrast, a leash of length $d$ is sufficient for the continuous Fréchet distance.}
  \label{fig_frechet_distance_upper_bound_example}
\end{figure}

Additionally, it is also a lower bound on the continuous Fréchet distance 
plus the distance of the longest legal jump of any frog. 
By increasing the number of points of a polygonal curve that 
overapproximates some other polygonal curve
this property can be used to compute the continuous Fréchet distance \cite{eiter_computing_1994}.

@@

\section{Algorithms}
\label{sec_algorithms}
% Chapter summary and structure
Several algorithms to compute the Fréchet distance of polygonal curves were proposed, 
starting from the original algorithm for the continuous variant by Alt and Godau in 1995 \cite{alt_computing_1995}.
The algorithm is based on a concept called free-space diagram and gives a baseline for newer improved versions, 
e.g., the version by Buchin et al. \cite{buchin_four_2017}. 
This chapter is structured as follows: 
first the original algorithm for the continuous Fréchet distance is described in \autoref{sec_original_algorithm}.
% then in \autoref{sec_improved_algorithm} a more recent improved algorithm for the same problem is given.
Afterwards, the modifications necessary to compute the weak variant are described in \autoref{sec_weak_algorithm}.
Finally, an algorithm to compute the discrete Fréchet distance is given in \autoref{sec_discrete_algorithm}.

@@

We start by looking at the simplest case for two polygonal curves with two vertices each, i.e., two line segments.
The free space is the set of all valid combinations of positions on $P$ and $Q$ that have a distance of at most $\varepsilon$.
Therefore, we define $F_\varepsilon = \{(s,t) \in [0,1]^2 \ | \ dist(P(s), Q(t)) \leq \varepsilon \}$.
Plotting $s$ and $t$ on a two-dimensional graph, while indicating all illegal combinations in 
another color, gives the free space diagram, see \autoref{fig_free_space}. \cite{alt_computing_1995}

@@

Computing the complete free space $F_\varepsilon$ is very compute intensive 
because each point in the continuous space needs to be computed. 
Using the convexity property of each cell in the free space,
we can observe that only a small constant number of points need to be computed per cell. 
These points define the legal regions on each boundary side of the cell, see \autoref{fig_legal_boundary_intervals_of_a_cell}. 
We do not need to know the exact shape of the free space 
because we travel in a monotonically increasing way through a convex space,
hence never entering any illegal regions.

@@

Due to the constant number of intersection points required per cell, 
the free space of a single cell can be computed in $\mathcal{O}(1)$ time.
Therefore, the complete free space of all cells can be computed in $\mathcal{O}(pq)$ time
because there are $p-1$ (respectively $q-1$) edges in $P$ (respectively $Q$).

@@

Another approach is to check all values of $\varepsilon$ where something ``interesting'' happens
until the smallest value of $\varepsilon$ is obtained where a monotonically increasing path 
from $(0,0)$ to $(p,q)$ in $F_\varepsilon$ exists.
We will call these the \textit{critical values} of $\varepsilon$, which are:
\begin{enumerate}
  \item the minimal value of $\varepsilon$ where $(0,0) \in F_\varepsilon$ and $(p,q) \in F_\varepsilon$.
  \item values of $\varepsilon$ where a new passage on the border edge 
        between two neighboring cells opens up.
  \item values of $\varepsilon$ where a new horizontal (respectively vertical) passage 
        between two non-neighboring cells opens up.
\end{enumerate}

@@

% Algorithms for different variants
\subsection{Algorithm for the Weak Fréchet Distance}
\label{sec_weak_algorithm}
For the weak Fréchet distance, as described in \autoref{sec_weak_frechet_distance},
the computation becomes less complex compared to the continuous Fréchet distance.
Specifically, we can ignore critical values of the third type, 
since it is no longer required to move monotonically 
and one could just go left or down in the free space diagram taking any arbitrary continuous path.
Therefore, the focus shifts towards critical values of the second type, 
those where new passages between neighboring cells open up.
Alt and Godau \cite{alt_computing_1995} proposed two algorithms to compute the weak Fréchet distance.

For both algorithms the problem is modeled as a grid based graph of $p$ by $q$ vertices, 
one for each cell of the free space diagram,
and edges connecting the vertices with their neighboring vertices.
There may be up to four neighboring vertices, namely, 
top, bottom, left, and right.
Additionally, $s$ is added as the start vertex and $t$ as the end vertex.
This results in an undirected Graph $G=(V,E)$ 
where $V = \{C_{i,j} \ | \ 0 \leq i \leq p, 0 \leq j \leq q \} \cup \{s,t\}$
and $E=\{(C_{i,j}, C_{i+1,j}) \ | \ \ 0 \leq i < p, 0 \leq j \leq q\} \cup \{(C_{i,j}, C_{i,j+1}) \ | \ \ 0 \leq i \leq p, 0 \leq j < q\} \cup \{(s, C_{0,0}), (C_{p,q}, t)\}$.
Each edge $(C_{i,j}, C_{i',j'})$ is assigned a critical minimal value of $\varepsilon$ 
such that there is a passage through the border between two cells in the free space. 
Furthermore, the minimal value of $\varepsilon$ such that $(0,0) \in F_\varepsilon$ is assigned to the first edge $(s, C_{0,0})$ 
and the minimal value of $\varepsilon$ such that $(p,q) \in F_\varepsilon$ is assigned to the last edge $(C_{p,q}, t)$. \cite{alt_computing_1995}

The first algorithm is again based on first solving the decision problem 
and then searching for the right $\varepsilon$ through binary search.
The decision problem is satisfied, if and only if there exists a path from $s$ to $t$ in $G$ 
with a maximum single edge value of $\varepsilon$.
This can be checked by removing all edges with values greater than $\varepsilon$ from $E$ 
and then checking if $s$ is still connected to $t$. 
This can be done through some graph traversal algorithm like breadth-first search or depth-first search
in $\mathcal{O}(pq)$ time. \cite{alt_computing_1995}
Since the number of critical values is no longer dominated by the third case,
rather by the second case of $\mathcal{O}(pq)$ values, 
the overall computation problem can be solved in $\mathcal{O}(pq \log (pq))$ time using binary search \cite{van_leusden_novel_2013}.

@@

\begin{mydef}
  \label{def_recursive_forumla_discrete_frechet_distance}
  The discrete Fréchet distance of polygonal curves $P' = (u_1, \dots, u_i)$ and $Q' = (v_1, \dots, v_j)$
  can be computed by
  \begin{align*}
    c(i,j) &= \begin{cases}
      dist(u_1, v_1), &\text{if } i=1 \text{and } j=1 \\
      \max \{c(i-1,1), dist(u_i, v_1)\}, &\text{if } i>1 \text{and } j=1 \\
      \max \{c(1,j-1), dist(u_1, v_j)\}, &\text{if } i=1 \text{and } j>1 \\
      \max \{c(i-1,j), c(i,j-1), c(i-1,j-1), dist(u_i, v_j)\}, &\text{if } i>1 \text{and } j>1
    \end{cases} \\
    &= \delta_{dF}(P',Q')
  \end{align*}
\end{mydef}

\section{Conclusion}
% Which version to use when
This work gives an overview on the Fréchet distance, 
its variants and algorithms to compute them. 
Several differences between the variants have been described 
and evaluated. 
In conclusion, it can be stated that computing the continuous 
Fréchet distance is more computationally expensive compared 
to its discrete and weak variants.
However, computing the continuous variant can be done efficiently
in practice by binary searching the bits of the desired accuracy directly
instead of computing the formally correct value. 
Alternatively, the discrete Fréchet distance can be calculated, 
since it bounds the continuous distance 
from below and above. 
In this way, the tolerance range can be narrowed down to a desired size.
